\documentclass[conference]{IEEEtran}
\IEEEoverridecommandlockouts
% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xcolor}
\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
\begin{document}

\title{Project Title}

\author{\IEEEauthorblockN{1\textsuperscript{st} Given Name Surname}
\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
\textit{IIIT Hyderabad}\\
Hyderabad, India \\
email address}
\and
\IEEEauthorblockN{2\textsuperscript{nd} Given Name Surname}
\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
\textit{IIIT Hyderabad}\\
Hyderabad, India \\
email address}
}

\maketitle

\begin{abstract}
Abstract of your work goes here... foobar
\end{abstract}

\begin{IEEEkeywords}
component, formatting, style, styling, insert
\end{IEEEkeywords}

\section{Introduction}
Explain the application with the use case.  You can illustrate the use with a
diagram here.

\section{Motivation}
In the current system architecture, which you explained in previous section,
what are the bottlenecks, in the software approach using CPU or GPU?  Make a
case for acceleration using FPGAs through profiling or some other argument. 

Identify the performance metrics and try to make your arguments tight using 
numbers as much as possible.

\section{Approach}

What is the architecture of the proposed system? What goes on CPU and what 
goes on FPGA? What is the overall data flow? Specifically, how do we move data
to FPGA and back? How do we store information on FPGA, like use BRAMs or DRAM?
Draw the architectural diagrams. 

\section{Project Plan}
How do you plan to approach the whole project? Divide the project into 
submodules with timelines and who does what. 

\section{Related Work}
So and so~\cite{trimberger15threeages} did so and so work.

Cite all the relevant papers in this section and write a line or two about them
here.
\section{Experimental Results}
What is your experimental analysis approach? What is the experimental setup?
What are the benchmark programs you are considering? What are the performance
metrics? What graphs and tables you would like to present and analyze?

\section{Conclusions}
That's how I changed the world :-)

\bibliographystyle{IEEEtran}
\bibliography{references}
\end{document}
